---
title: "Mental Health"
author: 'Cohort B: Alvaro Chinchayan, Leighton Li, Andrey Lifar, Yoki Liu, Yue Ping, Sherry Zuo'
subtitle: Capstone Project
date: "2/27/2020"
output:
  pdf_document:
    latex_engine: xelatex
---

Our main goal is to answer questions for:    
What's the overview of people's mental health problem?     
Can you predict whether a patient should be treated of his/her mental illness or not according to the value obtained based on our data?     
Is there a correlation between mental health and whether job lets them take them break/ alow them to work from home/remote worker?    
What can we get for the tweets' data? 


```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
library(ggplot2)
library(dplyr)
library(scales)
library(lubridate)
library(data.table)
library(skimr)
library(rtweet)
library(tidytext)
library(maps)
library(fastDummies)
library(corrplot)
library(tidyr)
library(magrittr)
library(ggthemes)
library(glmnet)
library(MASS)
library(rpart)
library(rpart.plot)
library(randomForest)
library(gbm)
theme_set(theme_bw())
library(caret)
library(leaps)
library(ggvis)
library(dvmisc)
```
Our first part will focus on the [OSMI Mental Health in Tech Surveys data](https://osmihelp.org/research)  
We merged 2016-2019 data into a new dataset by python, more code could see in the Mental_Health.ipynb file. We will use the merged dataset "mental_health" to do an overview of the mental illness    
We will do supervised machine learning focus on the year 2014 data  


Data Loading  
```{r}
#import data
data<-read_csv("~/Desktop/mental_health.csv")
data2014<-read_csv("~/Desktop/2014.csv")
```


Data Cleaning
```{r}
#remove first column since it's just the numbers of row
data<-data[,2:29]
```
```{r}
skim(data)
```
```{r}
#rename columns
names(data2014)[5:27]<-c("state","self_employed","family_history","mh_treatment", "interfere","company_size","remote","tech_company","mh_benefits","awareness_mh_benefits","mh_discuss","mh_resources", "anonymity_protected", "medical_leave_easy","mh_negative_consequence_flag","ph_negative_consequence_flag","mh_disscuss_coworker","mh_disscuss_supervisor","interview_mh_bringup", "interview_ph_bringup","mh_serious_ph","witness_mh_nc","comments")
```
```{r}
skim(data2014)
```
```{r}
#make a copy of our data
maindata<-data2014
#drop variables "Timestamp", “state”, “comments” just to make our lives easier.
maindata<-subset(maindata, select = -c(1,5,27))
```
```{r}
#keep columns names in lower case
names(maindata)[1:3]<-c("age","gender","country")
```
```{r}
maindata=data.table(maindata)
```

```{r}
#make word into lowercases in column gender
maindata$gender<-str_to_lower(maindata$gender)
#build gender group
male_str = c("androgyne", "cis male", "cis man", "m", "mail", "maile", "make", "mal", "male", "male (cis)", "male-ish", "malr", "man", "msle", "ostensibly male, unsure what that really means")
trans_str = c("a little about you", "agender", "all", "enby", "female (trans)", "fluid", "genderqueer", "guy (-ish) ^_^", "male leaning androgynous" , "nah", "neuter", "non-binary", "p", "queer", "queer/she/they", "something kinda male?", "trans woman", "trans-female")          
female_str = c("cis female", "cis-female/femme", "f", "femail", "femake", "female", "female (cis)", "woman")
#replace details
maindata$gender <- ifelse(maindata$gender %in% male_str, "M",ifelse(maindata$gender %in% female_str,"F",ifelse(maindata$gender %in% trans_str,"T",NA)))
```

```{r}
#so many countries only have 1 or 2 records, so we only keep countries has more than 10 countries
maindata %>% 
   filter(country %in% c('Australia','Canada','France','Germany','India','Ireland','Netherlands','United Kingdom','United States' )) -> maindata
```

```{r}
table(maindata$country)
```

```{r}
#remove other NAs, 236 interfere and 17 self-employed
maindata<-na.omit(maindata)
```

```{r}
skim(maindata)
```
```{r}
#there is one person list 329, one person list -1726, one person list -1, so delete those rows
maindata<-maindata[maindata$age!=329,]
maindata<-maindata[maindata$age!= -1726,]
maindata<-maindata[maindata$age!=-1,]
```
```{r}
names(maindata)
```

```{r}
maindata%>%
  ggplot(aes(x=age))+
  geom_bar(fill="red")+
  labs(title="Age Distribution", x="Age", y="Number of People")+
  theme(panel.background = element_rect(fill="transparent"),
        axis.line = element_line(colour = "black"))
# maindata%>%
#   group_by(age)%>%
#   tally() %>%
#   ggplot(aes(x=age,y = n))+
#   geom_bar(stat = 'identity', fill="red")+
#   labs(title="Age Distribution", x="Age", y="Number of People")+
#   theme(panel.background = element_rect(fill="transparent"), 
#         axis.line = element_line(colour = "black")) +
#   geom_text(aes(label = n))
```
```{r}
maindata%>%
   mutate(mh_treatment=ifelse(mh_treatment=="Yes", 1, 0))%>%
   group_by(interfere, gender)%>%
   summarize(proportion = sum(mh_treatment)/length(mh_treatment))%>%
   ggplot(aes(x=factor(interfere, levels=c("Never","Rarely","Sometimes","Often")), 
              y=proportion, fill=gender))+
      geom_bar(position = 'dodge', stat = 'identity')+
      labs(x="Work Interfere", y="Probability", 
           title="Probility of Mental Health Interfere based on Gender")+
      theme(panel.background = element_rect(fill="transparent"),
        axis.line = element_line(colour = "black"))
```
```{r}
maindata%>%
   mutate(mh_treatment=ifelse(mh_treatment=="Yes", 1, 0))%>%
   group_by(company_size, tech_company)%>%
   summarize(proportion = sum(mh_treatment)/length(mh_treatment))%>%
   ggplot(aes(x=factor(company_size, levels=c("1-5","6-25","26-100","100-500","500-1000","More than 1000")),
              y=proportion, fill=tech_company))+
      geom_bar(position = 'dodge', stat = 'identity')+
      labs(x="Company Size", y="Probability", 
           title="Probility of Mental Health Company Size base on Tech")+
      theme(panel.background = element_rect(fill="transparent"),
        axis.line = element_line(colour = "black"))
```
```{r}
maindata%>%
   mutate(mh_treatment=ifelse(mh_treatment=="Yes", 1, 0))%>%
   group_by(medical_leave_easy, remote)%>%
   summarize(proportion = sum(mh_treatment)/length(mh_treatment))%>%
   ggplot(aes(x=factor(medical_leave_easy, levels=c("Don't know","Very difficult","Somewhat difficult","Somewhat easy","Very easy")), y=proportion, fill=remote))+
      geom_bar(position = 'dodge', stat = 'identity')+
      labs(x="Leave Easy", y="Probability", 
           title="Probility of Mental Health Leave Easy based on remote")+
      theme(panel.background = element_rect(fill="transparent"),
        axis.line = element_line(colour = "black"))
```

```{r}
a=table(maindata$gender)
a
```
```{r}
str(a)
gender_count<-as.vector(a)
gender_percentage<-c("Female","Male","Transgender")
gender_count
gender_percentage
```
```{r}
pct1 <- round(gender_count/sum(gender_count)*100)
gender_percentage <- paste(gender_percentage, pct1) # add percents to labels
gender_percentage <- paste(gender_percentage,"%",sep="") # ad % to labels
pie(gender_count,labels = gender_percentage, col=rainbow(length(gender_percentage)),
   main="Pie Chart of Gender")
```
```{r}
#country could make a map in tableau
```
```{r}
b=table(maindata$self_employed)
b
```
```{r}
str(b)
self_employed_count<-as.vector(b)
self_employed_percentage<-names(b)
self_employed_count
self_employed_percentage
```
```{r}
pct2 <- round(self_employed_count/sum(self_employed_count)*100)
self_employed_percentage <- paste(self_employed_percentage, pct2) # add percents to labels
self_employed_percentage <- paste(self_employed_percentage,"%",sep="") # ad % to labels
pie(self_employed_count,labels = self_employed_percentage, col=rainbow(length(self_employed_percentage)),
   main="Pie Chart of Self_Employed")
```
```{r}
c=table(maindata$family_history)
c
```
```{r}
str(c)
family_history_count<-as.vector(c)
family_history_percentage<-names(c)
family_history_count
family_history_percentage
```
```{r}
pct3 <- round(family_history_count/sum(family_history_count)*100)
family_history_percentage <- paste(family_history_percentage, pct3) # add percents to labels
family_history_percentage <- paste(family_history_percentage,"%",sep="") # ad % to labels
pie(family_history_count,labels = family_history_percentage, col=rainbow(length(family_history_percentage)),
   main="Pie Chart of Family History of Mental Health")
```
```{r}
#Our outcome varaible
d=table(maindata$mh_treatment)
d
```
```{r}
str(d)
mh_treatment_count<-as.vector(d)
mh_treatment_percentage<-names(d)
mh_treatment_count
mh_treatment_percentage
```
```{r}
pct4 <- round(mh_treatment_count/sum(mh_treatment_count)*100)
mh_treatment_percentage <- paste(mh_treatment_percentage, pct4) # add percents to labels
mh_treatment_percentage <- paste(mh_treatment_percentage,"%",sep="") # ad % to labels
pie(mh_treatment_count,labels = mh_treatment_percentage, col=rainbow(length(mh_treatment_percentage)),
   main="Pie Chart of Whether seeking Mental Health Treatment")
```
```{r}
e=table(maindata$interfere)
e
```
```{r}
str(e)
interfere_count<-as.vector(e)
interfere_percentage<-names(e)
interfere_count
interfere_percentage
```
```{r}
pct5 <- round(interfere_count/sum(interfere_count)*100)
interfere_percentage <- paste(interfere_percentage, pct5) # add percents to labels
interfere_percentage <- paste(interfere_percentage,"%",sep="") # ad % to labels
pie(interfere_count,labels = interfere_percentage, col=rainbow(length(interfere_percentage)),
   main="Pie Chart of Interfere")
```
```{r}
f=table(maindata$company_size)
f
```
```{r}
str(f)
company_size_count<-as.vector(f)
company_size_percentage<-names(f)
company_size_count
company_size_percentage
```
```{r}
pct6 <- round(company_size_count/sum(company_size_count)*100)
company_size_percentage <- paste(company_size_percentage, pct6) # add percents to labels
company_size_percentage <- paste(company_size_percentage,"%",sep="") # ad % to labels
pie(company_size_count,labels = company_size_percentage, col=rainbow(length(company_size_percentage)),
   main="Pie Chart of Company Size")
```
```{r}
g=table(maindata$remote)
g
```
```{r}
str(g)
remote_count<-as.vector(g)
remote_percentage<-names(g)
remote_count
remote_percentage
```
```{r}
pct7 <- round(remote_count/sum(remote_count)*100)
remote_percentage <- paste(remote_percentage, pct7) # add percents to labels
remote_percentage <- paste(remote_percentage,"%",sep="") # ad % to labels
pie(remote_count,labels = remote_percentage, col=rainbow(length(remote_percentage)),
   main="Pie Chart of Remote")
```
```{r}
h=table(maindata$tech_company)
h
```
```{r}
str(h)
tech_company_count<-as.vector(h)
tech_company_percentage<-names(h)
tech_company_count
tech_company_percentage
```
```{r}
pct8 <- round(tech_company_count/sum(tech_company_count)*100)
tech_company_percentage <- paste(tech_company_percentage, pct8) # add percents to labels
tech_company_percentage <- paste(tech_company_percentage,"%",sep="") # ad % to labels
pie(tech_company_count,labels = tech_company_percentage, col=rainbow(length(tech_company_percentage)),
   main="Pie Chart of Tech Company")
```
```{r}
i=table(maindata$mh_benefits)
i
```
```{r}
str(i)
mh_benefits_count<-as.vector(i)
mh_benefits_percentage<-names(i)
mh_benefits_count
mh_benefits_percentage
```
```{r}
pct9 <- round(mh_benefits_count/sum(mh_benefits_count)*100)
mh_benefits_percentage <- paste(mh_benefits_percentage, pct9) # add percents to labels
mh_benefits_percentage <- paste(mh_benefits_percentage,"%",sep="") # ad % to labels
pie(mh_benefits_count,labels = mh_benefits_percentage, col=rainbow(length(mh_benefits_percentage)),
   main="Pie Chart of Mental Health Benefits")
```
```{r}
j=table(maindata$awareness_mh_benefits)
j
```
```{r}
str(j)
awareness_mh_benefits_count<-as.vector(j)
awareness_mh_benefits_percentage<-names(j)
awareness_mh_benefits_count
awareness_mh_benefits_percentage
```
```{r}
pct10 <- round(awareness_mh_benefits_count/sum(awareness_mh_benefits_count)*100)
awareness_mh_benefits_percentage <- paste(awareness_mh_benefits_percentage, pct10) # add percents to labels
awareness_mh_benefits_percentage <- paste(awareness_mh_benefits_percentage,"%",sep="") # ad % to labels
pie(awareness_mh_benefits_count,labels = awareness_mh_benefits_percentage, col=rainbow(length(awareness_mh_benefits_percentage)),
   main="Pie Chart of Awarenessof Mental Health Benefits")
```
```{r}
k=table(maindata$mh_discuss)
k
```
```{r}
str(k)
mh_discuss_count<-as.vector(k)
mh_discuss_percentage<-names(k)
mh_discuss_count
mh_discuss_percentage
```
```{r}
pct11 <- round(mh_discuss_count/sum(mh_discuss_count)*100)
mh_discuss_percentage <- paste(mh_discuss_percentage, pct11) # add percents to labels
mh_discuss_percentage <- paste(mh_discuss_percentage,"%",sep="") # ad % to labels
pie(mh_discuss_count,labels = mh_discuss_percentage, col=rainbow(length(mh_discuss_percentage)),
   main="Pie Chart of Mental Health Discussion")
```
```{r}
l=table(maindata$mh_resources)
l
```
```{r}
str(l)
mh_resources_count<-as.vector(l)
mh_resources_percentage<-names(l)
mh_resources_count
mh_resources_percentage
```
```{r}
pct12 <- round(mh_resources_count/sum(mh_resources_count)*100)
mh_resources_percentage <- paste(mh_resources_percentage, pct12) # add percents to labels
mh_resources_percentage <- paste(mh_resources_percentage,"%",sep="") # ad % to labels
pie(mh_resources_count,labels = mh_resources_percentage, col=rainbow(length(mh_resources_percentage)),
   main="Pie Chart of Mental Health Resources")
```
```{r}
m=table(maindata$anonymity_protected)
m
```
```{r}
str(m)
anonymity_protected_count<-as.vector(m)
anonymity_protected_percentage<-names(m)
anonymity_protected_count
anonymity_protected_percentage
```
```{r}
pct13 <- round(anonymity_protected_count/sum(anonymity_protected_count)*100)
anonymity_protected_percentage <- paste(anonymity_protected_percentage, pct13) # add percents to labels
anonymity_protected_percentage <- paste(anonymity_protected_percentage,"%",sep="") # ad % to labels
pie(anonymity_protected_count,labels = anonymity_protected_percentage, col=rainbow(length(anonymity_protected_percentage)),
   main="Pie Chart of Anonymity Mental Health Protection")
```
```{r}
n=table(maindata$medical_leave_easy)
n
```
```{r}
str(n)
medical_leave_easy_count<-as.vector(n)
medical_leave_easy_percentage<-names(n)
medical_leave_easy_count
medical_leave_easy_percentage
```
```{r}
pct14 <- round(medical_leave_easy_count/sum(medical_leave_easy_count)*100)
medical_leave_easy_percentage <- paste(medical_leave_easy_percentage, pct14) # add percents to labels
medical_leave_easy_percentage <- paste(medical_leave_easy_percentage,"%",sep="") # ad % to labels
pie(medical_leave_easy_count,labels = medical_leave_easy_percentage, col=rainbow(length(medical_leave_easy_percentage)),
   main="Pie Chart of Whether Medical Leave Easy")
```
```{r}
o=table(maindata$mh_negative_consequence_flag)
o
```
```{r}
str(o)
mh_negative_consequence_count<-as.vector(o)
mh_negative_consequence_percentage<-names(o)
mh_negative_consequence_count
mh_negative_consequence_percentage
```
```{r}
pct15 <- round(mh_negative_consequence_count/sum(mh_negative_consequence_count)*100)
mh_negative_consequence_percentage <- paste(mh_negative_consequence_percentage, pct15) # add percents to labels
mh_negative_consequence_percentage <- paste(mh_negative_consequence_percentage,"%",sep="") # ad % to labels
pie(mh_negative_consequence_count,labels = mh_negative_consequence_percentage, col=rainbow(length(mh_negative_consequence_percentage)),
   main="Whether Mental Health have Negative Consequence for Interview")
```
```{r}
p=table(maindata$ph_negative_consequence_flag)
p
```
```{r}
str(p)
ph_negative_consequence_flag_count<-as.vector(p)
ph_negative_consequence_flag_percentage<-names(p)
ph_negative_consequence_flag_count
ph_negative_consequence_flag_percentage
```
```{r}
pct16 <- round(ph_negative_consequence_flag_count/sum(ph_negative_consequence_flag_count)*100)
ph_negative_consequence_flag_percentage <- paste(ph_negative_consequence_flag_percentage, pct16) # add percents to labels
ph_negative_consequence_flag_percentage <- paste(ph_negative_consequence_flag_percentage,"%",sep="") # ad % to labels
pie(ph_negative_consequence_flag_count,labels = ph_negative_consequence_flag_percentage, col=rainbow(length(mh_negative_consequence_percentage)),
   main="Whether Physical Health have Negative Consequence for Interview")
```
```{r}
q=table(maindata$mh_disscuss_coworker)
q
```
```{r}
str(q)
mh_disscuss_coworker_count<-as.vector(q)
mh_disscuss_coworker_percentage<-names(q)
mh_disscuss_coworker_count
mh_disscuss_coworker_percentage
```
```{r}
pct17 <- round(mh_disscuss_coworker_count/sum(mh_disscuss_coworker_count)*100)
mh_disscuss_coworker_percentage <- paste(mh_disscuss_coworker_percentage, pct17) # add percents to labels
mh_disscuss_coworker_percentage <- paste(mh_disscuss_coworker_percentage,"%",sep="") # ad % to labels
pie(mh_disscuss_coworker_count,labels = mh_disscuss_coworker_percentage, col=rainbow(length(mh_disscuss_coworker_percentage)),
   main="Whether Disscuss Mental Health with Coworker")
```
```{r}
r=table(maindata$mh_disscuss_supervisor)
r
```
```{r}
str(r)
mh_disscuss_supervisor_count<-as.vector(r)
mh_disscuss_supervisor_percentage<-names(r)
mh_disscuss_supervisor_count
mh_disscuss_supervisor_percentage
```
```{r}
pct18 <- round(mh_disscuss_supervisor_count/sum(mh_disscuss_supervisor_count)*100)
mh_disscuss_supervisor_percentage <- paste(mh_disscuss_supervisor_percentage, pct18) # add percents to labels
mh_disscuss_supervisor_percentage <- paste(mh_disscuss_supervisor_percentage,"%",sep="") # ad % to labels
pie(mh_disscuss_supervisor_count,labels = mh_disscuss_supervisor_percentage, col=rainbow(length(mh_disscuss_supervisor_percentage)),
   main="Whether Disscuss Mental Health with Supervisor")
```
```{r}
s=table(maindata$interview_mh_bringup)
s
```
```{r}
str(s)
interview_mh_bringup_count<-as.vector(s)
interview_mh_bringup_percentage<-names(s)
interview_mh_bringup_count
interview_mh_bringup_percentage
```
```{r}
pct19 <- round(interview_mh_bringup_count/sum(interview_mh_bringup_count)*100)
interview_mh_bringup_percentage <- paste(interview_mh_bringup_percentage, pct19) # add percents to labels
interview_mh_bringup_percentage <- paste(interview_mh_bringup_percentage,"%",sep="") # ad % to labels
pie(interview_mh_bringup_count,labels = interview_mh_bringup_percentage, col=rainbow(length(interview_mh_bringup_percentage)),
   main="Whether Bring Up Mental Health into Interview")
```
```{r}
t=table(maindata$interview_ph_bringup)
t
```
```{r}
str(t)
interview_ph_bringup_count<-as.vector(t)
interview_ph_bringup_percentage<-names(t)
interview_ph_bringup_count
interview_ph_bringup_percentage
```
```{r}
pct20 <- round(interview_ph_bringup_count/sum(interview_ph_bringup_count)*100)
interview_ph_bringup_percentage <- paste(interview_ph_bringup_percentage, pct20) # add percents to labels
interview_ph_bringup_percentage <- paste(interview_ph_bringup_percentage,"%",sep="") # ad % to labels
pie(interview_ph_bringup_count,labels = interview_ph_bringup_percentage, col=rainbow(length(interview_ph_bringup_percentage)),
   main="Whether Disscuss Physical Health with Coworker")
```
```{r}
u=table(maindata$mh_serious_ph)
u
```
```{r}
str(u)
mh_serious_ph_count<-as.vector(u)
mh_serious_ph_percentage<-names(u)
mh_serious_ph_count
mh_serious_ph_percentage
```
```{r}
pct21 <- round(mh_serious_ph_count/sum(mh_serious_ph_count)*100)
mh_serious_ph_percentage <- paste(mh_serious_ph_percentage, pct21) # add percents to labels
mh_serious_ph_percentage <- paste(mh_serious_ph_percentage,"%",sep="") # ad % to labels
pie(mh_serious_ph_count,labels = mh_serious_ph_percentage, col=rainbow(length(mh_serious_ph_percentage)),
   main="Mental Health vs. Physical Health")
```
```{r}
v=table(maindata$witness_mh_nc)
v
```
```{r}
str(v)
witness_mh_nc_count<-as.vector(v)
witness_mh_nc_percentage<-names(v)
witness_mh_nc_count
witness_mh_nc_percentage
```
```{r}
pct22 <- round(witness_mh_nc_count/sum(witness_mh_nc_count)*100)
witness_mh_nc_percentage <- paste(witness_mh_nc_percentage, pct22) # add percents to labels
witness_mh_nc_percentage <- paste(witness_mh_nc_percentage,"%",sep="") # ad % to labels
pie(witness_mh_nc_count,labels = witness_mh_nc_percentage, col=rainbow(length(witness_mh_nc_percentage)),
   main="Whether Witness the Mental Health Negative Consequence")
```

```{r}
w<-table(maindata$country)
w
```
```{r}
str(w)
country_count<-as.vector(w)
country_percentage<-names(w)
country_count
country_percentage
```
```{r}
pct23 <- round(country_count/sum(country_count)*100)
country_percentage <- paste(country_percentage, pct22) # add percents to labels
country_percentage <- paste(country_percentage,"%",sep="") # ad % to labels
pie(country_count,labels = country_percentage, col=rainbow(length(country_percentage)),
   main="Pie Chart of Countries")
```
```{r}
dim(maindata)
```
```{r}
#write.csv(maindata,'maindata.csv')
```


Encoding Data
```{r}
#Make a copy to make us life easier and could use the categorical dataset when we need
dummydata<-maindata
```
```{r}
#Give numbers for those variable could have a order
dummydata$age=
  ifelse(dummydata$age<=20,1,
         ifelse(dummydata$age>20 & dummydata$age<=40 ,2,
                ifelse(dummydata$age>40 & dummydata$age<=60,3,4)))
dummydata$self_employed<-ifelse(dummydata$self_employed=="Yes", 1,0)
dummydata$family_history<-ifelse(dummydata$family_history=="Yes", 1,0)
dummydata$mh_treatment<-ifelse(dummydata$mh_treatment=="Yes", 1,0)
dummydata$interfere=
  ifelse(dummydata$interfere=='Never',1,
         ifelse(dummydata$interfere=='Rarely',2,
                ifelse(dummydata$interfere=="Sometimes",3,4)))
dummydata$company_size=
  ifelse(dummydata$company_size=='1-5',1,
         ifelse(dummydata$company_size=='6-25',2,
                ifelse(dummydata$company_size=="26-100",3,
                       ifelse(dummydata$company_size=="100-500",4,
                              ifelse(dummydata$company_size=="500-1000",5,6)))))
dummydata$remote<-ifelse(dummydata$remote=="Yes", 1,0)
dummydata$tech_company<-ifelse(dummydata$tech_company=="Yes", 1,0)
dummydata$mh_negative_consequence_flag=
  ifelse(dummydata$mh_negative_consequence_flag=='No',0,
         ifelse(dummydata$mh_negative_consequence_flag=='Maybe',1,2))
dummydata$ph_negative_consequence_flag=
  ifelse(dummydata$ph_negative_consequence_flag=='No',0,
         ifelse(dummydata$ph_negative_consequence_flag=='Maybe',1,2))
dummydata$mh_disscuss_coworker=
  ifelse(dummydata$mh_disscuss_coworker=='No',0,
         ifelse(dummydata$mh_disscuss_coworker=='Some of them',1,2))
dummydata$mh_disscuss_supervisor=
  ifelse(dummydata$mh_disscuss_supervisor=='No',0,
         ifelse(dummydata$mh_disscuss_supervisor=='Some of them',1,2))
dummydata$interview_mh_bringup=
  ifelse(dummydata$interview_mh_bringup=='No',0,
         ifelse(dummydata$interview_mh_bringup=='Maybe',1,2))
dummydata$interview_ph_bringup=
  ifelse(dummydata$interview_ph_bringup=='No',0,
         ifelse(dummydata$interview_ph_bringup=='Maybe',1,2))
dummydata$witness_mh_nc<-ifelse(dummydata$witness_mh_nc=="Yes", 1,0)
```
```{r}
skim(dummydata)
```

```{r}
#use this for some variable include "I don't know" or "Not sure" and for variable "gender"
#also use this for variable regions
dummydata<-dummy_cols(dummydata, select_columns = c("anonymity_protected", "awareness_mh_benefits","gender","medical_leave_easy", "mh_benefits", "mh_discuss", "mh_resources", "mh_serious_ph","country"))
```

```{r}
#after adding dummies, remove original categorical variables
#leave numeric variables
dummydata <- dummydata[-c(2:3,11:16,23)]
```

```{r}
dim(dummydata)
names(dummydata)
```
```{r}
skim(dummydata)
```
```{r}
#write.csv(dummydata,'dummydata.csv')
```


Model Choosing 
```{r fig.width=12, fig.height=12}
#Correlation Matrix
mh_c<-cor(dummydata)
corrplot(mh_c,
         type="upper",
         diag=F,
         method="color",
         order="hclust")
```
Split Dataset    
```{r}
set.seed(666)
# assign 270 random rows to the test set(around 30% of our dataset)
test_index <- sample(nrow(dummydata), 270) 
# now split
dummydata.test <- dummydata[test_index,]
dummydata.train <- dummydata[-test_index,]
```

Linear Regression 
**Preparation**
```{r}
# Intercept
intercept <- lm(mh_treatment ~ 1, data=dummydata.train)
summary(intercept)
```
```{r}
get_mse(intercept, var.estimate = FALSE)
```
```{r}
intercept.test <- lm(mh_treatment ~1, data = dummydata.test)
```
```{r}
get_mse(intercept.test, var.estimate = FALSE)
```
```{r echo=T, results='hide'}
# Fit the full model 
full.model <- lm(mh_treatment ~., data = dummydata.train)
summary(full.model)
```
```{r}
get_mse(full.model, var.estimate = FALSE)
```
```{r}
full.model.test <- lm(mh_treatment ~., data = dummydata.test)
```
```{r}
get_mse(full.model.test, var.estimate = FALSE)
```

Stepwise Regression
**Forward Selection** 
```{r echo=T, results='hide'}
forward.model <- stepAIC(intercept, direction = "forward", scope=list(upper=full.model, lower=intercept))
```
```{r}
forward.model$anova
```
```{r}
get_mse(forward.model)
```
```{r}
AIC <- as.data.frame(forward.model$anova$AIC)
names(AIC) <- "AIC"
AIC %>% 
    ggvis(x=~ c(1:10), y=~AIC) %>%
    layer_points(fill = ~ AIC) %>%
    add_axis("y", title = "AIC") %>% 
    add_axis("x", title = "Number of variables")
```
```{r}
yhat_test_forward <- predict(forward.model,dummydata.test)
```
```{r}
mse_test_forward <- mean((dummydata.test$mh_treatment-yhat_test_forward)^2)
mse_test_forward
```

**Backward Selection**
```{r echo=T, results='hide'}
backward.model <- stepAIC(full.model, direction = "backward")
```
```{r}
backward.model$anova
```
```{r}
get_mse(backward.model)
```
```{r}
AIC2 <- as.data.frame(backward.model$anova$AIC)
names(AIC2) <- "AIC2"
AIC2 %>% 
    ggvis(x=~ c(1:41), y=~AIC2 ) %>%
    layer_points(fill = ~ desc(AIC2)) %>%
    add_axis("y", title = "AIC") %>% 
    add_axis("x", title = "Number of variables eliminated")
```
```{r}
yhat_test_backward <- predict(backward.model,dummydata.test)
```
```{r}
mse_test_backward <- mean((dummydata.test$mh_treatment-yhat_test_backward)^2)
mse_test_backward
```

***

##### Penalized regression
```{r}
x_data <- model.matrix( ~ -1 + . -mh_treatment, dummydata)
x_train <- x_data[-test_index, ]
y_train <- dummydata$mh_treatment[-test_index]
x_test <- x_data[test_index, ]
y_test <- dummydata$mh_treatment[test_index]
```
**Ridge regression**    
```{r}
fit_ridge <- cv.glmnet(x_train, y_train, alpha = 0, nfolds = 10)
```
```{r}
yhat_train_ridge <- predict(fit_ridge, x_train, s = fit_ridge$lambda.min) 
mse_train_ridge <- mean((y_train - yhat_train_ridge)^2)
mse_train_ridge
```
```{r}
yhat_test_ridge <- predict(fit_ridge, x_test, s = fit_ridge$lambda.min) 
mse_test_ridge <- mean((y_test - yhat_test_ridge)^2)
mse_test_ridge
```
```{r}
# Plot cross-validation results
plot(fit_ridge)
```
```{r}
fit_ridge2 <- glmnet(x_train, y_train, alpha = 0)
plot(fit_ridge2, xvar = "lambda")
```

**Lasso regression**  
```{r}
fit_lasso <- cv.glmnet(x_train, y_train, alpha = 1, nfolds = 10)
```
```{r}
yhat_train_lasso <- predict(fit_lasso, x_train, s = fit_lasso$lambda.min) 
mse_train_lasso <- mean((y_train - yhat_train_lasso)^2)
mse_train_lasso
```

```{r}
yhat_test_lasso <- predict(fit_lasso, x_test, s = fit_lasso$lambda.min) 
mse_test_lasso <- mean((y_test - yhat_test_lasso)^2)
mse_test_lasso
```
```{r}
# Plot cross-validation results
plot(fit_lasso)
```
```{r message=FALSE, warning=FALSE}
fit_lasso2 <- glmnet(x_train, y_train, alpha = 1)
plot(fit_lasso2, xvar = "lambda")
```

More machine learning will in the python notebook.





